\documentclass[10pt,a4paper]{article}
\newcommand{\ReportShortTitle}{FULL PROJECT DOSSIER}
\input{suryagrid_report_preamble.tex}

\hypersetup{
  pdftitle={SuryaGrid AI - Full Implementation History and Execution Dossier},
  pdfauthor={SuryaGrid Project Team},
  pdfsubject={Day-by-day and commit-by-commit implementation history followed by the complete execution and agentic architecture}
}

\begin{document}
\teamtitlepage
  {Full Project Dossier}
  {Implemented History First, Then Complete Execution and Agentic Architecture}
  {A team-owned record of what was implemented, when it entered the repository, how the current
  frontend/backend/agent system connects, and the complete controlled path forward.}

\tableofcontents
\newpage

\part{Everything Implemented to Date}

\section{Verification Basis}

This dossier uses the following evidence hierarchy:

\begin{enumerate}
  \item the current local checkout at \code{main} commit \code{5bed3cd};
  \item a fresh fetch from both configured GitHub remotes;
  \item the GitHub repository commit list and pull-request metadata;
  \item full local commit messages, file lists, and change statistics;
  \item current code, routes, agents, data/model metadata, tests, and frontend build;
  \item the existing evidence matrix and technical reports.
\end{enumerate}

\begin{callout}{Repository history scope}
The main branch contains \textbf{37 commits} from 20 June through 7 July 2026. The fetched object
graph contains \textbf{39 unique commits}: the 37 main commits plus two side-branch commits not
merged into main. The implementation history below records all 37 main commits and identifies the
two non-main objects separately.
\end{callout}

\subsection{Current verified totals}

\begin{longtable}{@{}L{4.2cm}L{3.0cm}L{7.4cm}@{}}
\caption{Current verified project baseline on 9 July 2026.}\label{tab:verifiedtotals}\\
\toprule
\textbf{Measure} & \textbf{Verified value} & \textbf{Evidence}\\
\midrule
\endfirsthead
\toprule
\textbf{Measure} & \textbf{Verified value} & \textbf{Evidence}\\
\midrule
\endhead
\bottomrule
\endfoot
Main-branch commits & 37 & \code{git rev-list main --count}; GitHub main at \code{5bed3cd}\\
Unique fetched commits & 39 & \code{git rev-list --all --count}\\
Merged development PRs & 8 & GitHub PRs 2 through 9\\
Backend route operations & 61 & FastAPI route table under \code{/api/v1}\\
Agent modules & 17 & \code{backend/app/agents/*.py}, excluding \code{__init__.py}\\
Frontend feature routes & 12 & page directories under \code{frontend/app}\\
Generated frontend pages & 16 & Next.js production build output, including root and framework pages\\
Backend tests & 118 passed & \code{python -m pytest tests -q}, 19.30 seconds\\
Backend lint & all passed & \code{python -m ruff check app tests}\\
Frontend build & passed & Next.js 14.2.35 compile, type check, and static generation\\
Substation records & 344 & committed OSM-derived Bengaluru/Karnataka parquet\\
Current branch & \code{main} & both \code{origin/main} and \code{dbit/main} at \code{5bed3cd}\\
\end{longtable}

\section{Current Implemented System}

\subsection{Backend}

\begin{itemize}
  \item FastAPI application with health, weather, sites, predictions, timelines, energy,
        settlement, RL, Karnataka, source, ML, agent, location, DSM, system, Kaggle, and
        substation-orchestration route groups.
  \item SQLAlchemy async persistence with SQLite default and PostgreSQL support; Alembic migrations,
        repositories, audit/training/settlement records, and health record counts.
  \item Redis integration for cache/rate state, provider status, and optional scheduled ingestion.
  \item Open-Meteo live/current/archive integration and pvlib solar position, transposition,
        cell-temperature, PVWatts, clear-sky, and Erbs decomposition paths.
  \item Deterministic energy, DSM, risk, fuzzy-risk, reward/settlement research, RL environment,
        provider/API management, and multi-agent orchestration.
  \item Real-data ML build/train/inference pipelines with provenance, quality, model registry,
        cards, training manifests, and reproducible Kaggle ingestion.
  \item Substation-driven context service and five dedicated endpoints that pass the selected
        substation through weather, solar, cloud, generation, and DSM.
\end{itemize}

\subsection{Frontend}

\begin{itemize}
  \item Next.js 14 App Router with dashboard, predictions, timeline, energy, settlement, RL, Karnataka,
        locations, DSM, ML, data-sources, and system pages.
  \item A shared typed client in \code{frontend/lib/api.ts} with backend probe/offline handling and
        functions covering the 61-operation backend surface.
  \item Dark glass design system, metric/penalty cards, deviation/timeline charts, 3D SVG solar,
        energy-flow, and risk visuals, topbar/sidebar, and explicit backend-offline state.
  \item Substation workflow panel wired into Locations and DSM; model provenance and source status
        panels; Karnataka and RL views.
\end{itemize}

\subsection{Data and models}

\begin{itemize}
  \item Open-Meteo Bengaluru historical weather, NASA POWER cross-check, OSM substations, India
        national/regional load references, and multiple Kaggle solar/PV/load datasets.
  \item Production-marked irradiance and cloud-risk models with cards; DSM-breach decision support.
  \item Kaggle Bengaluru irradiance and cloud models; India PV/load models retained as non-local,
        non-production evidence because of domain shift.
  \item RL artifacts and research environments exist, but the authoritative production card is
        blocked for insufficient real local load, economics, and PV outcomes.
\end{itemize}

\subsection{Infrastructure and operations}

\begin{itemize}
  \item Dockerfiles and Docker Compose for frontend, backend, PostgreSQL, and Redis.
  \item GitHub Actions for backend tests, lint/format, frontend build, Pages, and an AWS CD path.
  \item Terraform for VPC, ECS/Fargate, RDS, ElastiCache, S3, CloudFront, security groups, and outputs.
  \item Single-instance Ubuntu deployment scripts, port changes, Nginx/subdomain configuration, and
        documentation. Managed AWS remains code-only until deployment is observed.
\end{itemize}

\section{Day-by-Day Implementation Record}

\subsection{20 June 2026 - Phase 1 MVP and first product surface}

\textbf{Five commits:} \code{6d08097}, \code{957f146}, \code{d4b484f},
\code{7e46fd8}, \code{6e85caf}.

\begin{itemize}
  \item Created the initial 94-file Phase 1 repository: solar nowcasting, DSM penalty prediction,
        fuzzy-risk engine, FastAPI backend, Next.js frontend, schemas, tests, documentation,
        Docker/development assets, and the initial implementation plan.
  \item Rebuilt the dashboard with metric cards, penalty status, deviation bars, timeline charts,
        badges, page navigation, and a professional data-display hierarchy.
  \item Added the animated 3D SVG solar panel, risk gauge, energy-flow visualization, glassmorphism
        theme, responsive layout, and design tokens.
  \item Added static export, a labelled client-side demonstration engine, GitHub Pages workflow,
        and startup support.
  \item Removed temporary/scratch artifacts as the first cleanup step.
\end{itemize}

\textbf{Day outcome:} a complete demonstrable MVP and visual product shell existed, but its core
data path was still primarily toy/synthetic and not yet the later real-data architecture.

\subsection{24 June 2026 - UI consolidation}

\textbf{One commit:} \code{e092af5}.

\begin{itemize}
  \item Unified predictions and timeline pages into the dark glass system and removed broken
        light-theme class dependencies.
  \item Consolidated global card, badge, table, button, scrollbar, and animation styles.
  \item Added the Topbar, live/demo connection indicator, typography, landing-page feature
        highlights, and consistent metric/deviation/penalty components.
\end{itemize}

\textbf{Day outcome:} the frontend became one coherent application instead of visually separate
pages.

\subsection{26 June 2026 - Real physics, CI/CD, settlement, and RL foundation}

\textbf{Thirteen commits, including six feature/fix commits and their merge commits.}

\begin{enumerate}
  \item \textbf{Runtime correctness and root serving} (\code{3627938}, merged by \code{016b41c}):
        fixed stale Redis health reporting, served the dashboard at root, removed the obsolete
        Pages workflow at that point, and updated run documentation.
  \item \textbf{Continuous integration} (\code{b872d09}, merged by \code{bb62673}):
        added Python 3.12 backend tests and Node 20 frontend build/type-check jobs.
  \item \textbf{Real nowcasting pipeline} (\code{5054782}, merged by \code{f13bc3d}):
        replaced the toy numeric path with Open-Meteo weather and pvlib physics; implemented
        solar position, POA, cell temperature, PVWatts DC/AC, clear-sky scheduling, excess-band
        DSM charging, deterministic risk, real weather/timeline APIs, and live frontend calls.
  \item \textbf{CI/CD hardening} (\code{6d7cf77}, \code{b283903}, merged by \code{8bb5e0a}):
        added Ruff lint/format, static-artifact validation, Pages deployment after CI, base-path
        detection, live URL verification, robust route-registration tests, and deployment docs.
  \item \textbf{Irradiance decomposition} (\code{a107eea}, merged by \code{3950741}):
        added automatic pvlib Erbs GHI-to-DNI/DHI fallback for providers without beam/diffuse data,
        while preserving measured DNI/DHI when available.
  \item \textbf{Full main-plan foundation} (\code{02ed09a}, merged by \code{70c75cd}):
        added reward/penalty/discount settlement research, energy balance, consumption profiles,
        provider rotation/quota tracking, RL digital twin and REINFORCE policy, policy weights,
        settlement/RL/energy APIs, and tests.
\end{enumerate}

\textbf{Day outcome:} SuryaGrid moved from a visual/toy MVP to a real-weather, physics-based,
continuously tested platform with the first complete deterministic decision loop and RL research
foundation.

\subsection{27 June 2026 - Persistence, Karnataka integration, real-time ingestion}

\textbf{Four commits:} \code{5ce7bfe}, \code{56beb46}, \code{f30e504}, \code{6bb54f8}.

\begin{itemize}
  \item Added persistent async SQLAlchemy storage, portable GUIDs, the project ER model,
        repositories, startup initialization, migrations, and health record counts.
  \item Added Open-Meteo archive ingestion and a real-data RL training path over historical
        irradiance-derived production; persisted training runs.
  \item Added Energy Balance, Settlement Engine, and RL Lab frontend pages and client contracts.
  \item Added multi-year archive windows, current weather, current ingestion, and opt-in APScheduler.
  \item Added Karnataka solar-site presets, seed/region endpoints, a BESCOM connector framework,
        Karnataka DSM framework, related APIs, and a Karnataka page.
  \item Kept the BESCOM/SLDC connector explicitly simulated until real metered access exists.
\end{itemize}

\textbf{Day outcome:} the system acquired persistence, historical training, real-time ingestion,
Karnataka-specific surfaces, and operational research workflows.

\subsection{6 July 2026 - Phase 1.7 real-data and honest ML rebuild}

\textbf{One major commit:} \code{95fb856}; 113 files changed.

\begin{itemize}
  \item Built a provenance-first data platform with source status, geography, data mode, domain
        shift, quality score, model cards, training manifests, and source registries.
  \item Built 26,304 hours of Bengaluru weather/solar history, a NASA POWER cross-check, 344 OSM
        substations, India load references, and solar/cloud/DSM/load training sets.
  \item Added solar, cloud-risk, DSM-breach, and load training/inference agents and endpoints.
  \item Marked local-unfit load/PV and RL honestly as non-production or blocked instead of
        promoting them from code existence alone.
  \item Added source, DSM, ML, agent, location, system, persistence, feature-engineering, and API
        management modules plus 16 Phase 1.7 tests.
\end{itemize}

\textbf{Day outcome:} the architecture became explicitly evidence-driven. ``Real'' was separated
from ``local'', ``estimated'', ``synthetic'', ``unavailable'', and ``production-ready''.

\subsection{7 July 2026 - Kaggle ML, AWS assets, deployment, evidence reports, substations}

\textbf{Thirteen commits on main.}

\begin{enumerate}
  \item \textbf{AWS architecture} (\code{507c6be}): Terraform for VPC, ECS/Fargate, RDS,
        ElastiCache, S3/CloudFront, security groups; AWS deployment workflow and architecture,
        app-flow, and deployment docs.
  \item \textbf{Single-instance deployment evolution} (\code{1070a11}, \code{d4c7e62},
        \code{5c158c1}, \code{7c0f22e}, \code{a17e3ef}, \code{04f61d5}): memory optimization for
        a small host, one-click Ubuntu deploy, backend port 8080, Nginx/subdomain attempts,
        direct-frontend fallback, and subdomain setup.
  \item \textbf{Code/data support} (\code{9b1c7eb}, \code{9efbe28}): formatted ML files and added
        a Kaggle download helper.
  \item \textbf{Kaggle real-data pipeline} (\code{16e6a4e}): ingested PV, Bengaluru irradiance,
        cloud-risk, and India load datasets; built four prefixed models/cards; added Kaggle APIs,
        tests, evidence docs, and an implementation report.
  \item \textbf{History integration} (\code{df372d2}): merged deployment/infra work with the
        Phase 1.7 Kaggle line.
  \item \textbf{Evidence report} (\code{360615f}): added the final technical report, evidence
        matrix, formula/DSM source documents, and hosted-app verification.
  \item \textbf{Substation-driven workflow} (\code{5bed3cd}): made a selected substation the
        central context; added context schema/service, seven-step orchestrator, five endpoints,
        15 tests, frontend workflow panel, agent/calculation trace, honest blocking, and committed
        the small OSM/grid feature parquets.
\end{enumerate}

\textbf{Day outcome:} the current \code{main} baseline was established: 61 APIs, 118 tests,
real-data model provenance, substation-driven orchestration, deployment options, and detailed
evidence documentation.

\section{Implemented Workflow as of the Baseline}

\begin{figure}[H]
\centering
\resizebox{\textwidth}{!}{
\begin{tikzpicture}[node distance=6mm]
\node[component] (ui) {Next.js UI\\station/site selection};
\node[component, right=of ui] (api) {Typed client\\FastAPI routes};
\node[agent, right=of api] (context) {Context and\\source registry};
\node[agent, right=of context] (weather) {Weather\\Open-Meteo / clear-sky};
\node[agent, below=8mm of weather] (solar) {Solar irradiance\\and PV forecast};
\node[agent, left=of solar] (cloud) {Cloud-risk\\classifier};
\node[agent, left=of cloud] (timeline) {Generation\\timeline};
\node[agent, left=of timeline] (dsm) {DSM and\\risk assessment};
\node[agent, below=8mm of cloud] (trace) {Orchestrator\\trace and blocks};
\node[store, left=of trace] (persist) {DB, model cards,\\provenance};
\node[component, left=of persist] (result) {API result\\cards and charts};

\draw[flow] (ui) -- (api);
\draw[flow] (api) -- (context);
\draw[flow] (context) -- (weather);
\draw[flow] (weather) -- (solar);
\draw[flow] (solar) -- (cloud);
\draw[flow] (cloud) -- (timeline);
\draw[flow] (timeline) -- (dsm);
\draw[flow] (dsm) |- (trace);
\draw[dataflow] (trace) -- (persist);
\draw[flow] (persist) -- (result);
\end{tikzpicture}}
\caption{Current implemented substation/site decision-support loop.}
\end{figure}

Current honest limits:

\begin{itemize}
  \item substation capacity is unavailable for all 344 OSM records;
  \item local measured PV and feeder/substation load are not connected;
  \item PV output is estimated from irradiance and configuration;
  \item official monetary DSM activation is pending source/version review;
  \item the production RL card remains blocked;
  \item authentication, tenant enforcement, alert delivery, read-only plant integration,
        HTTPS/operations evidence, and managed AWS deployment remain incomplete or unverified.
\end{itemize}

\section{Pull-Request and Branch Record}

\begin{longtable}{@{}C{1.2cm}L{5.2cm}L{5.0cm}L{3.5cm}@{}}
\caption{GitHub pull-request record relevant to main.}\label{tab:prs}\\
\toprule
\textbf{PR} & \textbf{Title / scope} & \textbf{Result} & \textbf{Main merge}\\
\midrule
\endfirsthead
\toprule
\textbf{PR} & \textbf{Title / scope} & \textbf{Result} & \textbf{Main merge}\\
\midrule
\endhead
\bottomrule
\endfoot
2 & Redis health and root path & merged & \code{016b41c}\\
3 & CI backend tests and frontend build & merged & \code{bb62673}\\
4 & Real Open-Meteo + pvlib nowcasting and DSM & merged & \code{f13bc3d}\\
5 & Harden CI/CD and Pages & merged & \code{8bb5e0a}\\
6 & Erbs fallback for GHI-only data & merged & \code{3950741}\\
7 & Settlement, energy balance, API agent, RL & merged & \code{70c75cd}\\
8 & Persistent DB, historical RL, new UI & merged & \code{56beb46}\\
9 & Karnataka/BESCOM, multi-year and current ingestion & merged & \code{6bb54f8}\\
10 & CodeRabbit-generated unit-test branch & open; not in main & side commit \code{32eec8a}\\
\end{longtable}

\section{Complete Main-Branch Commit Ledger}

\begin{footnotesize}
\begin{longtable}{@{}C{1.9cm}C{2.1cm}L{6.0cm}L{5.1cm}@{}}
\caption{All 37 commits on main, in chronological order.}\label{tab:commits}\\
\toprule
\textbf{Commit} & \textbf{Date} & \textbf{Repository summary} & \textbf{Implementation meaning}\\
\midrule
\endfirsthead
\toprule
\textbf{Commit} & \textbf{Date} & \textbf{Repository summary} & \textbf{Implementation meaning}\\
\midrule
\endhead
\bottomrule
\endfoot
\code{6d08097} & 20 Jun & Phase 1 complete MVP & Initial backend, frontend, agents, DSM/fuzzy risk, tests, docs\\
\code{957f146} & 20 Jun & Frontend UI overhaul & Dashboard, cards, deviation and timeline visuals\\
\code{d4b484f} & 20 Jun & Temporary-file cleanup & Repository hygiene\\
\code{7e46fd8} & 20 Jun & 3D SVG/glass UI & Solar, risk, energy visuals and theme\\
\code{6e85caf} & 20 Jun & GitHub Pages and mock engine & Static demonstration/deployment path\\
\code{e092af5} & 24 Jun & Cohesive dark glass UI & Design-system and page unification\\
\code{3627938} & 26 Jun & Redis health/root fix & Correct live health and root serving\\
\code{016b41c} & 26 Jun & Merge PR 2 & Integrated runtime fix\\
\code{b872d09} & 26 Jun & CI workflow & Backend tests and frontend build\\
\code{bb62673} & 26 Jun & Merge PR 3 & Integrated CI\\
\code{5054782} & 26 Jun & Real nowcasting + DSM & Open-Meteo, pvlib, real timeline, deterministic risk\\
\code{f13bc3d} & 26 Jun & Merge PR 4 & Integrated real nowcasting\\
\code{6d7cf77} & 26 Jun & Harden CI/CD and Pages & Ruff, artifact/live checks, deployment docs\\
\code{b283903} & 26 Jun & OpenAPI route test fix & FastAPI-version-stable route verification\\
\code{8bb5e0a} & 26 Jun & Merge PR 5 & Integrated hardened pipeline\\
\code{a107eea} & 26 Jun & Erbs GHI fallback & Physically valid DNI/DHI derivation\\
\code{3950741} & 26 Jun & Merge PR 6 & Integrated Erbs fallback\\
\code{02ed09a} & 26 Jun & Full platform foundation & Settlement, reward, energy, RL, API agent\\
\code{70c75cd} & 26 Jun & Merge PR 7 & Integrated full-platform modules\\
\code{5ce7bfe} & 27 Jun & Persistence, historical RL, new UI & DB, archive training, energy/settlement/RL pages\\
\code{56beb46} & 27 Jun & Merge PR 8 & Integrated persistent data/UI\\
\code{f30e504} & 27 Jun & Karnataka/BESCOM and current data & Multi-year/current ingestion and state workflow\\
\code{6bb54f8} & 27 Jun & Merge PR 9 & Integrated Karnataka expansion\\
\code{95fb856} & 6 Jul & Phase 1.7 real-data ML & Provenance-first datasets, agents, cards, honest gates\\
\code{507c6be} & 7 Jul & AWS IaC and documentation & ECS/RDS/Redis/S3/CloudFront intended stack\\
\code{1070a11} & 7 Jul & 2 GB host optimization & Small-instance Compose tuning\\
\code{d4c7e62} & 7 Jul & Ubuntu deploy script & One-command server deployment workflow\\
\code{5c158c1} & 7 Jul & Backend port 8080 & Host/proxy port alignment\\
\code{7c0f22e} & 7 Jul & Nginx proxy & Subdomain reverse-proxy attempt\\
\code{a17e3ef} & 7 Jul & Direct frontend fallback & Resolved port-80 conflict path\\
\code{04f61d5} & 7 Jul & Subdomain setup & Nginx site automation\\
\code{9b1c7eb} & 7 Jul & ML formatting & Ruff code-format cleanup\\
\code{9efbe28} & 7 Jul & Kaggle download helper & Dataset acquisition support\\
\code{16e6a4e} & 7 Jul & Kaggle pipeline/models/report & Four datasets/models, APIs, cards, evidence\\
\code{df372d2} & 7 Jul & History merge & Combined infrastructure and Kaggle lines\\
\code{360615f} & 7 Jul & Evidence-based final report & Hosted/repository verification and formula sources\\
\code{5bed3cd} & 7 Jul & Substation-driven workflow & Context, orchestration, endpoints, UI panel, 118-test baseline\\
\end{longtable}
\end{footnotesize}

\subsection{Fetched commits not in main}

\begin{itemize}
  \item \code{85c7753}: side-branch CI commit associated with the Redis/root-path branch history.
  \item \code{32eec8a}: CodeRabbit-generated tests on open PR 10; not merged into main.
\end{itemize}

\section{Current Verification Result}

On 9 July 2026, the current checkout was revalidated:

\begin{itemize}
  \item \code{python -m pytest tests -q}: \textbf{118 passed}.
  \item \code{python -m ruff check app tests}: \textbf{all checks passed}.
  \item \code{npm run build}: \textbf{compiled, linted, type-checked, and generated 16 pages}.
\end{itemize}

This verifies the current repository baseline. It does not automatically verify production
uptime, official regulatory interpretation, external datasets not committed to the repository,
managed AWS deployment, or real plant telemetry.

\clearpage
\input{suryagrid_execution_architecture_body.tex}

\end{document}
